SMT-Boosted Security Types for Low-Level MPC

### 2025-04-28 esop25/slides.tex
checkpoint

 Verifiable \emph{entailment} $\eqs_1 \models \eqs_2$ means that any model of $\eqs_1$ is a model
 of $\eqs_2$. Models of $\prog$ correspond exactly to valid runs of $\prog$...

@@

  Entailment is a mechanism for verifying protocol properties. If an interpretation
  of a protocol entails a property, it holds in all protocol runs. 
$$
\begin{array}{c}
  \toeq{\sumthree} \wedge \ttt{out} \eop \mx{ss1}{1} + \mx{ss1}{2} + \mx{ss1}{3}\\ \models\\
  \ttt{out} \eop \sx{1}{1} \fplus \sx{2}{2} \fplus \sx{3}{3}
\end{array}
$$

@@

  Verifying equational properties also supports verification of confidentiality.
  It is well-known that expressions of the form:
  $$
  e - \rx{w}{\cid}
  $$
  are a means of encrypting $e$ using $\rx{w}{\cid}$ as a one-time-pad in any
  size field. This can be leveraged in typing. 
  $$    
  \inferrule[Encode]
  {\eqs \models \toeq{e} \eop \toeq{e'} - \rx{w}{\cid}\\
   \eqj{R}{\eqs}{e'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{e}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
  $$
  \begin{itemize}
  \item The \emph{ciphertype} $\cty{\rx{w}{\cid}}{\ty}$ indicates the computation
    results in a value encrypted with $\rx{w}{\cid}$.
  \item $\ty$ is a conservative approximation of the dependencies in $e'$.
  \item The \emph{randomness environment} $R;\{ \rx{w}{\cid} \}$ enforces
    linearity.
  \end{itemize}

>>>>

 Verifiable \emph{entailment} $\eqs_1 \models \eqs_2$ means that any model of $\eqs_1$ is a model
 of $\eqs_2$. Models of $\prog$ correspond exactly to valid runs of $\prog$, therefore...

@@

  ... entailment is a mechanism for verifying protocol properties. If an interpretation
  of a protocol entails a property, it holds in all protocol runs. 
$$
\begin{array}{c}
  \toeq{\sumthree} \wedge \ttt{out} \eop \mx{ss1}{1} + \mx{ss1}{2} + \mx{ss1}{3}\\ \models\\
  \ttt{out} \eop \sx{1}{1} \fplus \sx{2}{2} \fplus \sx{3}{3}
\end{array}
$$

@@

  Verifying equational properties also supports verification of confidentiality.
  It is well-known that expressions of the form:
  $$
  (e - \rx{w}){\cid}
  $$
  are a means of encrypting $e$ using $\rx{w}{\cid}$ as a one-time-pad in any
  size field. This can be leveraged in typing. 
  $$    
  \inferrule[Encode]
  {\eqs \models \toeq{e} \eop \toeq{e'} - \rx{w}{\cid}\\
   \eqj{R}{\eqs}{e'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{e}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
  $$
  \begin{itemize}
  \item The \emph{ciphertype} $\cty{\rx{w}{\cid}}{\ty}$ indicates the computation
    results in a value encrypted with $\rx{w}{\cid}$.
  \item $\ty$ is a conservative approximation of the dependencies in $e'$.
  \item The \emph{randomness environment} $R;\{ \rx{w}{\cid} \}$ enforces
    linearity.
  \end{itemize}
